Realizing temporal graphs from fastest travel times

### 2023-09-25 Figures/fig-motivationExample.tex
Final version of the STACS submission

\begin{tikzpicture}[xscale=2]
	%%%S_uv
	\node[vert,label=below:$u$] (v1) at (1,0) {};
	\node[vert] (v2) at (2,0) {};
	\node[vert,label=below:$w$] (v3) at (3,0) {};
	\node[vert] (v4) at (4,0) {};
	\node[vert,label=below:$v$] (v5) at (5,0) {};
	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);

>>>>

\begin{tikzpicture}[xscale=2]
	%%%S_uv
	\node[vert,label=below:$u$] (v1) at (1,0) {};
	\node[vert] (v2) at (2,0) {};
	\node[vert,label=below:$w$] (v3) at (3,0) {};
	\node[vert] (v4) at (4,0) {};
	\node[vert,label=below:$v$] (v5) at (5,0) {};
	\draw (v1) -- node[label=above:$1$] {} (v2) -- node[label=above:$3$] {}  (v3) -- node[label=above:$5$] {} (v4) -- node[label=above:$7$] {} (v5);
	\draw (v1) to [out=80,in=100,distance=2cm] node[label=above:$9$] {} (v3);
